ms2

### 2017-05-25 ms2/ms2.Rmd
ms2 hrr

hrr = read_tsv('../../db/hrr/hrr.tsv') %>%
  select(zipcode, hrr) %>%
  left_join(zipcodes, by='zipcode') %>%
  left_join(regions, by='state')

@@

state_ineq = read_years('data/state_ineq_%i.tsv')
hrr_ineq = read_years('data/hrr_ineq_%i.tsv')
```

@@

## Inequality among users does not correlate well

@@

```{r nzgini_mean}
all_ineq %>%
  ggplot(aes(x=mean_cpb, xmin=mean_cpb-sem_cpb, xmax=mean_cpb+sem_cpb,
             y=mean_nzgini, ymin=mean_nzgini-sem_nzgini, ymax=mean_nzgini+sem_nzgini,
             color=region, label=state_abbreviation)) +
  geom_point() +
  geom_linerange() +
  geom_errorbarh(height=0) +
  geom_text(nudge_x=0.04) +
  xlab('mean claims per beneficiary') +
  ylab('mean Gini coefficient') +
  theme_minimal()
```

@@

multivariate_term = 'nzgini'
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  # swo> "mean" is a confusing name
  bind_rows(
    linear_model(x, dep, 'mean') %>% mutate(model='univariate'),
    linear_model(x, dep, c('fnz', multivariate_term)) %>% mutate(model='multivariate'),
    linear_model(x, dep, multivariate_term) %>% mutate(model='uni_nzg'),
    spearman_model(x, dep, 'mean') %>% mutate(model='spearman')
  ) %>%
    mutate(n_data=nrow(x))
}

@@

## Univariate Gini

```{r}
filter(results, model=='uni_nzg', term=='nzgini') %>%
  arrange(p.value) %>%
  mutate(adj.p=p.adjust(p.value, method='bonferroni')) %>%
  select(bug, drug_group, estimate, p.value, adj.p, n) %>%
  kable
```

## Univariate

@@

```{r univariate_models}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n) %>%
  kable
```

```{r}
results %>%
  filter(model=='univariate', term=='mean') %>%
  interval_plot()
```

```{r}
results %>%
  filter(model=='univariate') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  ggplot(aes(x=estimate, y=-log10(p.adj))) + geom_point() +
  geom_hline(yintercept=-log10(0.05), col='red')
```

@@

```{r hrr_univariate_models}
hrr_results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

## Multivariate

@@

```{r multivariate_models}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

```{r}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  interval_plot()
```

```{r}
results %>%
  filter(model=='multivariate') %>%
  filter(term == multivariate_term) %>%
  mutate(bug_drug=interaction(bug, drug_group)) %>%
  ggplot(aes(x=p.value, y=estimate, color=drug_group)) +
  geom_point() +
  scale_color_brewer(palette='Set1')
```

And what about looking at multivariate only for ones that passed the threshold for univariate?

```{r eval=FALSE}
sig_bug_drug = results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r}
hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_multivariate_models}
sig_bug_drug = hrr_results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r nzgini_cpb_drug}
cbbPalette <- c("#000000", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")
state_ineq %>%
  ggplot(aes(x=mean, y=nzgini, color=drug_group)) +
  geom_point() +
  ylab('Gini coefficient among users') + xlab('claims per beneficiary') +
  theme_minimal() +
  scale_color_manual(values=cbbPalette)
```

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  filter(bug %in% c('E. coli', 'Eb. cloacae', 'CNST', 'MSSA', 'MRSA', 'S. pneumoniae')) %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=drug_group, shape=bug)) +
  geom_point() +
  xlab('claims per beneficiary')
```

@@

```{r ecoli_quin, cache=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()

@@

```{r ecoli_bactrim}
ecoli_bactrim_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') #%>%
  #filter(!is.na(mean_percent_nonsusceptible))

@@

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='S. pneumoniae', drug_group=='macrolide') %>%
  filter(!is.na(mean_percent_nonsusceptible)) %>% 
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  theme_minimal()
```

@@

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Eb. cloacae', drug_group=='quinolone') %>%
  filter(!is.na(mean_percent_nonsusceptible)) %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  theme_minimal()
```

@@

```{r mssa_clinda}
dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='MSSA', drug_group=='clindamycin') #%>%
  #filter(!is.na(mean_percent_nonsusceptible))

@@

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='MRSA', drug_group=='clindamycin') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  #scale_x_continuous(limits=c(0.08, 0.2), breaks=c(0.08, 0.1, 0.15, 0.2)) +
  #ylim(10, 45) +
  xlab('clindamycin claims per beneficiary') + ylab('mean percent nonsusceptible MRSA isolates') +
  theme_minimal()
```

>>>>

# Use the zipcode-HRR mapping from 2011
hrr = read_tsv('../../db/hrr/hrr.tsv') %>%
  filter(year==2011) %>%
  select(zipcode, hrr) %>%
  left_join(zipcodes, by='zipcode') %>%
  left_join(regions, by='state')

@@

state_ineq = read_years('data/state_ineq_%i.tsv') %>%
  rename(cpb=mean) %>%
  group_by(state, drug_group) %>%
  summarize(cpb=mean(cpb), fnz=mean(fnz), nzg=mean(nzgini)) %>%
  ungroup()

hrr_ineq = read_years('data/hrr_ineq_%i.tsv') %>%
  rename(cpb=mean) %>%
  group_by(hrr, drug_group) %>%
  summarize(cpb=mean(cpb), fnz=mean(fnz), nzg=mean(nzgini)) %>%
  ungroup()
```

@@

```{r}
all_ineq %$%
  cor.test(mean_cpb, mean_fnz, method='spearman')
```

## The two inequality metrics not correlate well

@@

```{r nzgini_mean}
all_ineq %>%
  ggplot(aes(x=mean_fnz, xmin=mean_fnz-sem_fnz, xmax=mean_fnz+sem_fnz,
             y=mean_nzgini, ymin=mean_nzgini-sem_nzgini, ymax=mean_nzgini+sem_nzgini,
             color=region, label=state_abbreviation)) +
  geom_point() +
  geom_linerange() +
  geom_errorbarh(height=0) +
  geom_text(nudge_x=0.04) +
  xlab('mean fraction with at least one claim') +
  ylab('mean Gini coefficient') +
  theme_minimal()
```

The correlation exists but it's much less strong.

```{r}
all_ineq %$%
  cor.test(mean_fnz, mean_nzgini, method='spearman')
```

There is an intermediate correlation between claims per beneficiary and the Gini coefficient (see below), so in multivariable regressions I will use those two (rather than CPB and Gini).

```{r}
all_ineq %$% cor.test(mean_cpb, mean_nzgini, method='spearman')
```

@@

uni_term = 'cpb' # univariable explanatory term
multi_term = 'nzg' # multivariable explanatory term (along with fnz)
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  bind_rows(
    linear_model(x, dep, uni_term) %>% mutate(model='uni'),
    linear_model(x, dep, c('fnz', multi_term)) %>% mutate(model='multi'),
    spearman_model(x, dep, uni_term) %>% mutate(model='spearman')
  ) %>%
    mutate(n_data=nrow(x))
}

@@

## Univariable

@@

```{r uni_models}
results %>%
  filter(model=='uni', term==uni_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n) %>%
  kable
```

```{r}
results %>%
  filter(model=='uni', term==uni_term) %>%
  interval_plot()
```

```{r}
results %>%
  filter(model=='uni') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  ggplot(aes(x=estimate, y=-log10(p.adj))) + geom_point() +
  geom_hline(yintercept=-log10(0.05), col='red')
```

@@

```{r hrr_uni_models}
hrr_results %>%
  filter(model=='uni', term==uni_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

## Multivariable

@@

```{r multi_models}
results %>%
  filter(model=='multi', term==multi_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

```{r}
results %>%
  filter(model=='multi', term==multi_term) %>%
  interval_plot()
```

```{r}
results %>%
  filter(model=='multi', term==multi_term) %>%
  mutate(bug_drug=interaction(bug, drug_group)) %>%
  ggplot(aes(x=p.value, y=estimate, color=drug_group)) +
  geom_point() +
  scale_color_brewer(palette='Set1')
```

And what about looking at multivariate only for ones that passed the threshold for univariable?

```{r eval=FALSE}
sig_bug_drug = results %>%
  filter(model=='uni', term==uni_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

results %>%
  filter(model=='multi', term==multi_term) %>%
  right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r}
hrr_results %>%
  filter(model=='multi', term==multi_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_multi_models}
sig_bug_drug = hrr_results %>%
  filter(model=='uni', term==uni_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

hrr_results %>%
  filter(model=='multi', term==multi_term) %>%
  right_join(sig_bug_drug, by=c('bug', 'drug_group')) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r nzgini_cpb_drug}
cbbPalette <- c("#000000", "#D55E00", "#CC79A7", "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")
state_ineq %>%
  ggplot(aes(x=cpb, y=nzg, color=drug_group)) +
  geom_point() +
  ylab('Gini coefficient among users') + xlab('claims per beneficiary') +
  theme_minimal() +
  scale_color_manual(values=cbbPalette)
```

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  filter(bug %in% c('E. coli', 'Eb. cloacae', 'CNST', 'MSSA', 'MRSA', 'S. pneumoniae')) %>%
  ggplot(aes(x=cpb, y=mean_percent_nonsusceptible, color=drug_group, shape=bug)) +
  geom_point() +
  xlab('claims per beneficiary')
```

@@

```{r ecoli_quin, eval=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()

@@

```{r ecoli_bactrim, eval=FALSE}
ecoli_bactrim_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') #%>%
  #filter(!is.na(mean_percent_nonsusceptible))

@@

```{r, eval=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='S. pneumoniae', drug_group=='macrolide') %>%
  filter(!is.na(mean_percent_nonsusceptible)) %>% 
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  theme_minimal()
```

@@

```{r, eval=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Eb. cloacae', drug_group=='quinolone') %>%
  filter(!is.na(mean_percent_nonsusceptible)) %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  theme_minimal()
```

@@

```{r mssa_clinda, eval=FALSE}
dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='MSSA', drug_group=='clindamycin') #%>%
  #filter(!is.na(mean_percent_nonsusceptible))

@@

```{r, eval=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='MRSA', drug_group=='clindamycin') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  #scale_x_continuous(limits=c(0.08, 0.2), breaks=c(0.08, 0.1, 0.15, 0.2)) +
  #ylim(10, 45) +
  xlab('clindamycin claims per beneficiary') + ylab('mean percent nonsusceptible MRSA isolates') +
  theme_minimal()
```
